\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with continuum detection in the lensing FR-II galaxy 3C220.3

### 2015-06-27 skeleton.tex
Up to molecular gas mass section

\documentclass{emulateapj}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$ = 3 $\rightarrow$ 2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K km s$^{-1}$ pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{$^{-1}$}
%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
%\shortauthors{Leung and Riechers}

\begin{document}
\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685}
\author{No name}
%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers\altaffilmark{2}}
%\affil{Astronomy Department, Cornell Unviersity}
%\altaffiltext{1}{tleung@astro.cornell.edu}
%\altaffiltext{2}{dr@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$ = 0.8 \Msun (\LpU)\pmOne. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are found predominantly at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
 far-infrared (FIR) wavelengths. Large sky surveys (e.g., HERMES, HATLAS) with submm facilities have lead to growing consensus
  of the observable properties of SMGs. SMGs are a population of galaxy at high redshifts that are typically dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne). (e.g., Lagache et al. 2005, cite more recent). \par
  To characterize the properties of the gas reservoirs in the ISM, where active star formation takes place, CO rotational lines have been commonly used as a tracer due to its high abundance in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}. Recent observations of the CO line of SMGs at $z \sim$ 1-3 have  
provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun. In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, the lensing amplification boost the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite). \par
One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
type-2 quasar host at $z$ = 2.221 being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685. The two lenses are separated by 1\farcs5. The redshift of the background SMG has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceiving evidence of AGN activity in the SMG, as well as the 
existence of a type-2 quasar.
The background SMG has a lensing-magnified flux density of $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy, which is one of 
the
brightest known even among lensed
SMGs.

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy. This paper is organized as follows: in \S \ref{sec:obs}, we describe the
observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
detection of the CO line in the background galaxy as well as the continuum in the foreground galaxy; in \S
\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
conclude our findings by comparing to other SMGs at high redshifts.

@@

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
\rarr 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s\pmOne). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam\pmOne.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
%MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
% So integrated - peak should be approx. the extended components ~ (7.18 - 5.56 mJy)
%      --- Integrated:   7.18 +/- 0.69 mJy
%      --- Peak:         5.56 +/- 0.54 mJy/beam

%Deconvolution size bigger than expected (if just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam\pmOne.
In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}. This figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.

@@

\subsection{New results: \CO line emission}
We detect \CO line emission toward the background SMG SMM J0939. Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission. Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and FWHM of 541.65 $\pm$ 31.91 km s\pmOne. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the \CO detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the \CO 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$378.1 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore the primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).

@@

We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
values of the best-fit lens model \citet{Haas14} performed on Keck K-band near-infrared image. For each of
these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
reported in their paper. The axial ratios of the lenses are restricted to $q_{\rm lens} > 0.3$. We initialize 512
walkers and 6000 steps to identify the best-fit model parameters.
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_bestfit}
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_bestfit}
\caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
In this two lenses model, we initialize the lenses' positions using the values reported by \citet{Haas14}. Left:
Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at 2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
show the negative residuals. \label{fig:lens}}
\end{figure}

@@

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}

We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{\rm cont}$ = 104.2106 GHz 
(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
hence we expect the continuum to be dominated by emissions from the foreground galaxy.

====== I will edit this: \\
Previous studies suggest that at 104 GHz, contributions from the radio core dominates over that from the radio lobes and jets (cite), thus we 
expect the emission from the core component to dominate our continuum measurement; however, the integrated flux density is measured 
to be 7.18 $\pm$ 0.69 mJy. Since the orientation of the synthesized beam aligns with the axis along the 
lobes of the radio galaxy as shown in Figure \ref{fig:cont}, we interpret the difference in the peak flux 
density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
includes emissions from the lobes. Furthermore, the contours of the 104 GHz continuum are
centered on the north lobe of the radio galaxy in the overlay image, this further supports our argument. 
\citet{Mullin06a} report an upper limit on the radio core of 0.17 mJy at 4.6 GHz, whereas \citet{Haas14} 
report a detection of the radio core of 0.8 mJy at 9 GHz, as shown in Figure \ref{fig:SED}.\\
====== Please keep on reading from here.

We fit the SED of the radio galaxy using previous data listed in Table \ref{tab:SEDdataRadio}, following Equation (1) by \citet{Cleary07a}, the fit can be expressed as a functional form:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution. 
\\ ====== I will edit this ====
In their paper, they limit $\nu_t >$ 1 MHz, 30 GHz $< \nu_c^{\rm lobe}$ 3000 GHz, which give best-fit parameters, and we use their parameters to plot the fit, and we extrapolate to 104 GHz, which is = blah mJy, which is consistent with our continuum measurement. Therefore the 10$\sigma$ detection of the partially resolved continuum emission suggests a 
non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
emission. 
\\ ==================
\input{table_SED}

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{Figure shows the SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed blue line and 
the dashed dot magenta line correspond to the best-fit SED of the background SMG, using an optically thick model, and an 
optically thin model, respectively. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
\end{figure}

>>>>

%\documentclass{emulateapj}
\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\usepackage{hyperref}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$ = 3 $\rightarrow$ 2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K km s$^{-1}$ pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{$^{-1}$}
\newcommand\tna{\,\tablenotemark{a}}
\newcommand\tnb{\,\tablenotemark{b}}
\newcommand\tnc{\,\tablenotemark{c}}
\newcommand\tnd{\,\tablenotemark{d}}
\newcommand\tne{\,\tablenotemark{e}}
\newcommand\tnf{\,\tablenotemark{f}}
\newcommand\tng{\,\tablenotemark{g}}

%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
%\shortauthors{Leung and Riechers}

\begin{document}
\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
continuum detection in the lensing FR-II galaxy 3C220.3}
\author{No name}
%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
%\affil{Astronomy Department, Cornell Unviersity}
%\altaffiltext{1}{tleung@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$ = 0.8 \Msun (\LpU)\pmOne. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
 far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HERMES, HATLAS) with sub-(mm) facilities have led to growing consensus
  of the observable properties of SMGs (cite). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne). (e.g., Lagache et al. 2005, cite more recent). \par
  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}. Recent observations of the CO line of SMGs at $z \sim$ 1-3 have  
provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun. In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite). \par
One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently
the brightest known lensed
SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceivable evidence of AGN activity in this SMG, as well as the identification of a type-2 quasar.

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy. This paper is organized as follows: in \S \ref{sec:obs}, we describe the
observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
detection of the CO line in the background galaxy as well as the continuum in the foreground galaxy; in \S
\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
conclude our findings by comparing to other SMGs at similar redshifts.

@@

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
\rarr 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s\pmOne). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam\pmOne.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
%MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam\pmOne.
In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}. This figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.

@@

\subsection{New results: \CO line emission}
We detect \CO line emission toward the background SMG SMM J0939. Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission. Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 541.65 $\pm$ 31.91 km s\pmOne. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the \CO detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the \CO 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$378.1 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore the primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).

@@

We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
values of the best-fit lens model \citet{Haas14} performed on Keck K-band near-infrared image. For each of
these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
reported in their paper. The axial ratios of the lenses are restricted to $q_{\rm lens} > 0.3$. We initialize 512
walkers and 6000 steps to identify the best-fit model parameters.
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit0771}
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit0771}
\caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
In this two lenses model, we initialize the lenses' positions using the values reported by \citet{Haas14}. Left:
Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at 2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
show the negative residuals. \label{fig:lens}}
\end{figure}

@@

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}
In the theory of synchrotron emission, continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises and dominates the flux density at higher frequencies (cite). Consequently, we expect the peak flux density in our continuum detection of $S_{\rm 104GHz}$ = 5.56 $\pm$ 0.54 mJy to be dominated by the unresolved core component of the foreground FR-II. On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission. This is plausible given that the orientation of the synthesized beam in our observations aligns with the axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to estimate the flux density of the lobes at the frequency of our continuum measurement. For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) is indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs. All measurements are plotted in Figure \ref{fig:SED}. \input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobes can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.

The resulting fit is shown in Figure \ref{fig:SED}, the extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement. The 10$\sigma$ detection of the continuum thereby suggests
non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
emission. Furthermore, the contours of the 104 GHz continuum are
centered on the northern lobe as illustrated by the overlay image in Figure \ref{fig:cont}, this further supports our argument. This finding is consistent with a recent study by \citet{Hardcastle08a}, where a few radio galaxies blah blah. At the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{The SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
Black dots represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red dots at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The purple line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed purple line and 
the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
\end{figure}
